\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Sayan Dasgupta}

\section{Work experience}

\begin{eventlist}

\item{Mar 2019 -- Present}
  {Embibe}
  {Principal Data Scientist}
  Managing 3 Teams. Consumer Intelligence, Search Relevance and Data Science Platform with a focus to drive learning outcomes for millions of students. \\
  15+ members across teams, comprising of Data Scientists, Data Engineers and ML Engineers. \\
  Consumer Intelligence team built and delivered state of the art recommendation platform, by assessing current academic and behavioral state of student leveraging different knowledge tracing models, and then taking the student through a learning journey to help her achieve her goal. \\
  Search relevance team was responsible for launch of lightning fast personalised search, with improved relevance algorithms. \\
  
  
  
\item{Oct 2017 -- Mar 2019}
  {Careem}
  {Member of technical Staff in Data Science}
  Responsible for detection and prevention of fraud on the driver side leveraging ML.
  %% Building machine learning models for identifcation of fraud also working with the team in architecting products to streamline surfacing, validating and taking action against fraudulent drivers.

\item{Oct 2016 -- Sept 2017}
     {C1X Inc}
     {Senior Manager of Data Science}
Team Architected data science and analytics platform using AWS EMR(ETL), MySQL, Apache Superset (BI) and reduced time to insights to less than hour from previously being multiple days. \\
Implemented RTB enrichment based on extensive A/B testing on ad impression bid prices. \\

\item{May 2013 -- Sept 2016}
     {Linkedin}
     {Senior Data Scientist \\ Anti-abuse engineering Team}

Designed and implemented machine learning models to identify fake accounts on a social network in
order to prevent fraud, spam, and abuse on the site. The work involved designing and implementing
an extensible framework to enhance the model by applying different modeling technique, including
new features, and benchmarking them. \\[2pt]
Trained and implemented classifers to detect spam in short text like name and headline. \\[2pt]
 Designed and implemented a framework that takes outcome of classification models for abuse detection
available on hdfs and takes appropriate action against them online. \\[2pt]
Worked on detection and prevention of scraping on Linkedin. \\[2pt]
Designed and implemented intrusion detection system on Linkedin production system. \\[2pt]
%% Models were implemented in production using R, Python, Java, Pig.

\item{Jan 2012 -- Apr 2013}
     {Symphony (Shopzilla)}
     {Senior Data Scientist}

Forecasting Revenue Per Click of each keyword that is being marketed to acquire SEM traffic
leveraging big data technologies and statistical/machine-learning models. \\[2pt]
%% Optimizing the bid for each keyword leveraging the google bid simulator data.

\item{Aug 2010 - Jan 2012}
     {Innovation Labs, 24/7 Inc}
     {Senior Analytics Consultant}

Built and deployed machine learning  models utilizing click stream data to score visitor propensity to attrite or purchase. \\[2pt]
%% Network Analysis of online journeys and corresponding web content to optimize website design at-
%% tributes and for robust A/B testing.\\[2pt]
%%  Market Basket Analysis using Apriori Algorithm was used to suggest products for upsell/cross sell. \\[2pt]
\end{eventlist}

\personal
    {Bangalore, India}
    {+919591374000}
    {dasgupta.sayan@gmail.com}

\section{Education}

\begin{yearlist}

\item{2007 -- 2009}
     {Masters in Statistics}
     {Indian Statistical Institute, Delhi}

\item{2004 -- 2007}
     {Statistics Honours, Bachelor of Science}
     {St Xavier's College, Kolkata}

\end{yearlist}

\section{Invited Talks}

\begin{yearlist}

\item{2016}
  { (\href{http://wecommer.com/en/conference/2242/speaker/49862}{Smart Data summit Dubai})}
  {Presented our work on leveraging data science to prevent abuse on Linkedin at Smart Data Summit, Dubai}

\item{2015}
     { (\href{https://www.youtube.com/watch?v=fcdnaEACICc}{Facebook Spam at Scale conference})}
     {Presented the work on detecting spam in short text at Spam at Scale Conference hosted by Facebook.}

\end{yearlist}

\section{Miscellaneous}

\begin{itemize}
\item IIT JAM (Statistics) 2007 All India Rank 15
\item Granted patent for \href{https://patents.google.com/patent/US10204307B1/en}{Classification of members in a social networking service}. Patent Number: US10204307B1
\end{itemize}

\section{Software skills}

\begin{factlist}

\item{Programming and Scripting}
  { R, Python, Bash, SQL}
  
\item{Big Data technologies}
  {Hadoop, Spark, Hive, Splunk, Pig}
  
\item{Miscellaneous}
  {AWS Stack, Docker, Git, Python-Flask, GNU Emacs}

\end{factlist}

\section{Reference}
Available on request.

\end{document}
