%%%%%%%%%%%%%%%%%
% This is a two-column CV template based on moderncv.cls
%%%%%%%%%%%%%%%%

% environment
\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.95]{geometry}
\usepackage{tabularx}
\usepackage{mathpazo}
% \usepackage{hyperref}
\usepackage{xcolor}

% \usepackage[hyphens]{url}
% \usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}

% macro
\renewcommand*{\labelitemi}{-}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[5][1mm]{
    \subsection{#2} \vspace{-1.5mm}
    \small{
    \begin{tabularx}{\textwidth}{LR}
        {\itshape #3} & {\itshape #4, #5}
    \end{tabularx}
    }
    \par\addvspace{#1}
}

\newcommand*{\sayaneducationentry}[4][1mm]{ % Four arguments: optional spacing, date, degree, institute
    \par\addvspace{#1} % Add vertical spacing
    \begin{tabularx}{\textwidth}{@{}p{1mm}X@{}} % Define a 2-column table with fixed width for the first column
        & {\textsc{#2}} \\ % First row: Date (small caps), first column left empty
        & {\bfseries #3} \\ % Second row: Degree (bold)
        & {\itshape #4} \\ % Third row: Institute (italic)
    \end{tabularx}
}

\newcommand*{\invitedtalk}[4][1mm]{ % Four arguments: optional spacing, year, conference, description
    \par\addvspace{#1} % Add vertical spacing
    {\bfseries #2} \\ % First row: Year in bold
    {\bfseries #3} \\ % Second row: Conference name in bold
    \noindent{\itshape #4} % Third row: Description in italics
}

\newcommand*{\educationentry}[4][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3} & {\bfseries #4} \\
    \end{tabularx}
    {\itshape #2}
    \par\addvspace{#1}
}

\newcommand{\achievement}[1]{%
    \item #1
}

\newenvironment{yearlist}{%
    \renewcommand\item[4][]{%
    \textsc{##2} & \textbf{##3} \\
    \ifstrempty{##1}{}{& \textsc{##1} \\}
    & \textit{##4}\medskip\\}
    \tabularx{\linewidth}{rX}}
    {\endtabularx}

\newcommand*{\scoreentry}[3][2.5mm]{
    {\bfseries #2} \\
    {\itshape #3}
    \par\addvspace{#1}
}
% \renewcommand*{\namefont}{\fontsize{14}{18}\selectfont}
% \renewcommand*{\titlefont}{\fontsize{10}{12}\selectfont}

% preamble
\firstname{Sayan}
\familyname{Dasgupta}
% \address{Bengaluru, India}{}
\mobile{(+91)9591374000}
\email{dasgupta.sayan@gmail.com}
\social[linkedin]{sayandasgupta}
% \social[github]{github}

% document
\begin{document}
\maketitle
\vspace{-10.0mm}

% left column
\begin{minipage}[t]{0.64\textwidth}
\section{EXPERIENCE}

\experienceentry{Citrix, Netscaler Business Unit}{Principal Data Scientist}{Dec 2020 -- Present}{BLR, India}
\vspace{-5mm}
\begin{small}
\begin{itemize}
    \item Architected and developed \textbf{\textit{Netscaler Copilot}}, a RAG-based AI platform enabling question-answering across Netscaler products, reducing time-to-resolution (TTR) for customers by 20\%.
    \item Designed and implemented guardrails to protect the system from adversarial attacks.
    \item Created evaluation metrics (BERT Score and BLEU Score) to measure the AI model’s performance.
    \item Developed models to identify volumetric and sophisticated \textbf{Account Takeover attacks}, leveraging statistical and machine learning techniques.
    \item Built sentiment analysis models to analyze customer feedback and identify key areas for improvement.
    \item Developed the \textbf{\textit{Netscaler Voice of Customer (VoC) Dashboard}} to visualize insights and track progress on improvements.
\end{itemize}
\end{small}

\vspace{0.25mm}

\experienceentry{Reliance JIO Embibe}{Principal Data Scientist}{Apr 2019 -- Mar 2020}{BLR, India}
\vspace{-5mm}
\begin{itemize}
    \item Led a 10-member data science team to develop an AI-based learning platform.
    \item Built a learning journey recommendation system, increasing user engagement from 16 minutes to 23 minutes (\textbf{43\%}) and improving learning outcomes by 20\%.
    \item Developed and deployed \textbf{\textit{Bayesian Knowledge Tracing (BKT)}} models to measure student mastery of various concepts.
    \item Built \textbf{2PL IRT} models to understand question difficulty and discrimination for test design.
    \item Conducted A/B testing to validate the impact of the models on the platform.
\end{itemize}
\vspace{0.25mm}

\experienceentry{Careem}{MTS in Data Science}{Apr 2018 -- Mar 2019}{Dubai, UAE}
\vspace{-5mm}
\begin{itemize}
    \item Developed Careem’s ML-based driver fraud detection system, significantly increasing cost savings.
    \item Created statistical and ML models to identify phantom trips.
    \item Built a system to augment automated trip-flagging with manual review by local teams, enabling timely intervention.
\end{itemize}
\vspace{0.5mm}

\experienceentry{C1X Inc}{Senior Manager of Data Science}{Oct 2016 -- Sept 2017}{BLR, India}
\vspace{-5mm}
\begin{itemize}
    \item Implemented real-time bidding (RTB) enrichment via extensive A/B testing on ad impression bid prices.
    \item Architected a data science and analytics platform using AWS, EMR (ETL), MySQL, and Apache Superset (BI). Reduced time to insights from multiple days to under one hour.
\end{itemize}
\vspace{0.5mm}

\experienceentry{LinkedIn}{Senior Data Scientist}{May 2013 -- Sept 2016}{BLR, India}
\vspace{-5mm}
\begin{itemize}
    \item Designed and implemented machine learning models to detect fake accounts, preventing fraud and spam. Reduced touch back rate to \textbf{1\%} from north of 4\%.
    \item Reduced invitation spam by \textbf{18\%} over control group leveraging the member identity model.
    \item Built end-to-end model training pipelines, handled feature engineering, and led model evaluation.
    \item Trained and deployed classifiers to detect spam in short text fields such as user names and headlines.
\end{itemize}

\experienceentry{Shopzilla, Symphony}{Senior Data Scientist}{Jan 2012 -- Apr 2013}{BLR, India}
\vspace{-5mm}
\begin{itemize}
    \item Forecasted Revenue Per Click for SEM keywords using big data technologies and statistical/machine-learning models.
\end{itemize}

\experienceentry{Innovation Labs, 24/7 Inc}{Senior Analytics Consultant}{Aug 2010 -- Jan 2012}{BLR, India}
\vspace{-5mm}
\begin{itemize}
    \item Built and deployed machine learning models utilizing clickstream data to score visitor propensity to churn or purchase.
\end{itemize}

\end{minipage}
\hspace{0.01\textwidth}
% right column
\begin{minipage}[t]{0.32\textwidth}

\section{EDUCATION}
\sayaneducationentry{2007 -- 2009}{Master of Statistics}{Indian Statistical Institute, Delhi}
\sayaneducationentry{2004 -- 2007}{B.Sc. in Statistics (Honours)}{St. Xavier's College, Kolkata}

\vspace{-3.0mm}
{\section{Invited Talks}}
\invitedtalk{2015}{Facebook Spam at Scale}{Presented research on detecting spam in short text.}
\invitedtalk{2016}{Smart Data Summit, Dubai}{Discussed leveraging data science to prevent abuse on LinkedIn.}

\vspace{-3.0mm}
\section*{Achievements}
\begin{itemize}
    \achievement{Secured \textbf{All India Rank 15} in IIT JAM (Statistics) 2007.}
    \achievement{Granted a patent for “Classification of members in a social networking service.” \textbf{Patent No: US10204307B1}.}
    \achievement{Received the prestigious \textbf{Rajiv Sinha Technology Award} at Netscaler.}
\end{itemize}

\vspace{-3.0mm}
\section*{Technical Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} Python, R, SQL, Bash, \LaTeX
    \item \textbf{Machine Learning:} scikit-learn, Prophet, XGBoost, Statsmodels
    \item \textbf{Deep Learning:} PyTorch
    \item \textbf{Generative AI:} 
    \begin{itemize}
        \item \textbf{LLM Frameworks:} LangChain, Autogen, FAISS, Qdrant
        \item \textbf{Models \& APIs:} Azure OpenAI, Anthropic Claude
    \end{itemize}
    \item \textbf{Big Data:} Spark, Hadoop, Hive
    \item \textbf{Cloud Platforms:} Azure, AWS
\end{itemize}

\vspace{-3.0mm}
\section*{Selected Technical Writeups}
\begin{itemize}
    \item \href{https://sayan.github.io/dl-lecture-notes/neural_network_and_deep_learning/pytorch/06_pytorch_back_propagation_linear_layer.html}{\textcolor{blue}{\underline{Backpropagation in PyTorch}}}
    \item \href{https://sayan.github.io/dl-lecture-notes/neural_network_and_deep_learning/logreg/logreg}{\textcolor{blue}{\underline{Logistic Regression}}}
\end{itemize}

\vspace{-3.0mm}
\section*{References}
Available upon request.

\end{minipage}

\end{document}
